\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-11-17 chapters/patients.tex
Indicated comments Reinhold and Fabien

\chapter{Case studies}
\label{sec:patients}
\section{Introduction}

@@

\textcite{Severens2014} evaluated the visual Hex-o-Spell~\cite{Treder2010} on 5
participants with \ac{als} and showed that this visual oddball interface optimized
for gaze-independence can outperform a tactile \ac{bci}.
While this speaks to the power of visual paradigms even in groups that are
expected to have eye motor impairment, they did not verify the gaze direction
of participants during the experiment.
It was suggested that participants were performing overtly.
Participants with \ac{als} also had a substantially lower accuracy than healthy
controls (58\% vs 88\%).

@@

The \ac{eeg} was band-pass filtered between 0.5 and 16 Hz.
Bad channels were rejected using the RANSAC algorithm~\cite{Fischler1981}
and visual inspection.
Next, the \ac{eeg} was re-referenced to the average of mastoid electrodes TP9
and TP10, and \ac{ica} was performed to reject artifactual components based on
correlation with the \ac{eog} or by visual inspection.
Epochs were cut from -0.1 to 0.9s relative to stimulus onset, and no baseline
correction was performed.

Eye tracking data was cleaned by fusing left and right gaze into one channel
for the horizontal and vertical gaze position.
If both were present for a given sample, the fused channel was the mean of both
values.
If at a given sample either the left or the right eye was not detected for a
given channel, the value of the other one was adopted.
If both were missing, the gaze position remained unset at that time point, and no
interpolation was performed.

@@

However, \ac{wcble} did not improve \ac{tlda} performance in the free \ac{vsa} setting, but
XDAWNCov+TS+LDA performance was slightly lower here (though not
significantly).
(\ac{wcble} 74.15\%, XDAWNCov+TS+LDA 71.88\%, \ac{tlda} 74.27\%).
More interestingly, we noticed that performances of the decoders in free
\ac{vsa} were close to those in the overt \ac{vsa}.
A substantial decrease in performance from the overt setting to the free
setting was observed for
subjects PC3 and PC4.
For PB2, who also relied on covert \ac{vsa} during the uncued free \ac{vsa}
setting, there was no decrease in performance.

@@

Individuals with all but the most severe gaze impairments will likely retain
some degree of gaze direction in visual \ac{bci} operation, which can
drastically boost performance.
Subject PB2 exemplifies this: his free \ac{vsa} performance is on par with his
overt \ac{vsa} performance, although eye tracking showed that he relied mostly
on overt \ac{vsa} when cued to do so, and mostly on covert \ac{vsa} when
gaze was uncued.
This is also supported by our results on cross-condition calibration presented
in \cref{sec:patients/outcomes/cross}, which show that leveraging residual
eye motor control to fixate targets during the calibration phase can improve
performance in some settings.
This is likely due to the increased P3 component amplitude in overt \ac{vsa},
which improves the discriminative power of a classifier trained on this data.
Cueing this overt gaze fixation only during the calibration phase leaves the user
free to operate in the manner that is most comfortable for them in the
operation phase.
Early VEPs in the training data could also contribute in those cases where the participant was not
able to perform covert \ac{vsa} with central gaze fixation.

>>>>

\chapter{Case studies}
\label{sec:patients}
\epigraph{I knew there would be a lot of unexpected issues involved with
patient experiments, but I never thought there would be interference from baby
goats in the experiment room.}{Juliette}

\section{Introduction}

@@

\textcite{Severens2014} evaluated the visual Hex-o-Spell~\cite{Treder2010} on 5
participants with \ac{als} and showed that this visual oddball interface optimized
for gaze-independence can outperform a tactile \ac{bci}.
While this speaks to the power of visual paradigms even in groups that are
expected to have eye motor impairment, they did not verify the gaze direction
of participants during the experiment.
It was suggested that participants were performing overtly.
Participants with \ac{als} also had a substantially lower accuracy than healthy
controls (58\% vs. 88\%).

@@

The \ac{eeg} was band-pass filtered between 0.5 and 16 Hz.
Bad channels were rejected using the RANSAC algorithm~\cite{Fischler1981}
and visual inspection.
Next, the \ac{eeg} was re-referenced to the average of mastoid electrodes TP9
and TP10, and \ac{ica} was performed to reject artifactual components based on
correlation with the \ac{eog} or by visual inspection.
Epochs were cut from -0.1 to 0.9s relative to stimulus onset, and no baseline
correction was performed in order to meet the assumptions.

Eye tracking data was cleaned by fusing left and right gaze into one channel
for the horizontal and vertical gaze position.
If both were present for a given sample, the fused channel was the mean of both
values.
If at a given sample either the left or the right eye was not detected for a
given channel, the value of the other one was adopted.
If both were missing, the gaze position remained unset at that time point, and no
interpolation was performed of the employed classifiers.

@@

However, \ac{wcble} did not improve \ac{tlda} performance in the free \ac{vsa} setting, but
XDAWNCov+TS+LDA performance was slightly lower here (though not
significantly).
(\ac{wcble} 74.15\%, XDAWNCov+TS+LDA 71.88\%, \ac{tlda} 74.27\%).
More interestingly, we noticed that performances of the decoders in free
\ac{vsa} were close to those in the overt \ac{vsa}.\todo{qualitative}
A substantial decrease in performance from the overt setting to the free
setting was observed for
subjects PC3 and PC4.\todo{qualitative}
For PB2, who also relied on covert \ac{vsa} during the uncued free \ac{vsa}
setting, there was no notable decrease in performance.\todo{qualitative}

@@

Individuals with all but the most severe gaze impairments will likely retain
some degree of gaze direction in visual \ac{bci} operation, which can
drastically boost performance.
Subject PB2 exemplifies this: his free \ac{vsa} performance is on par with his
overt \ac{vsa} performance, although eye tracking showed that he relied mostly
on overt \ac{vsa} when cued to do so, and mostly on covert \ac{vsa} when
gaze was uncued.\todo{qualitative}
This is also supported by our results on cross-condition calibration presented
in \cref{sec:patients/outcomes/cross}, which show that leveraging residual
eye motor control to fixate targets during the calibration phase can improve
performance in some settings.
This is likely due to the increased P3 component amplitude in overt \ac{vsa},
which improves the discriminative power of a classifier trained on this data.
Cueing this overt gaze fixation only during the calibration phase leaves the user
free to operate in the manner that is most comfortable for them in the
operation phase.
Early VEPs in the training data could also contribute in those cases where the participant was not
able to perform covert \ac{vsa} with central gaze fixation.

### 2024-11-17 chapters/stbf_struct.tex
Indicated comments Reinhold and Fabien

	\subsubsection{Shrunk covariance estimation}
	\label{sec:stbf-struct/methods/shrunk-cov}
	The shrinkage covariance estimator creates a better-conditioned inversion matrix problem and generally performs better when applied to unseen data.
	The estimators for the covariance and inverse covariance are given by:
	\begin{equation}
    \hat{\mat{C}}_\alpha =
    (1-\alpha) \hat{\mat{C}}_\text{emp}
    + \alpha\frac{\text{Tr}(\hat{\mat{C}}_\text{emp})}{CS}\mathbb{I}
		\label{eq:shrinkage}
	\end{equation}
	\begin{equation}
    \widehat{\mat{C}^{-1}}_\alpha =
    \hat{\mat{C}}^+_\alpha
		\label{eq:stbf-struct/shrinkage-inv}
	\end{equation}
	with $0<\alpha<1$.
	Analogous to $L_2$ regularization of the beamforming problem,
	shrinkage reduces the ratio between the smallest and largest eigenvalues
	of the covariance matrix by strengthening the diagonal.
	\cref{fig:kronlda-covs}c and \cref{fig:kronlda-covs}d respectively show examples of the
	shrunk estimator of the covariance and the inverse covariance matrices.

@@

	The \ac{eeg} recorded at 2048Hz was re-referenced off-line to the average of the mastoids.
	The reference electrodes were dropped from the analysis.
	Data were subsequently filtered between 0.5Hz and 16Hz using forward-backward
	filtering with a fourth-order Butterworth IIR filter.
	The \ac{eeg} signal was corrected for ocular artifacts using Independent Component
	Analysis (ICA) by rejecting components that correlated with the bipolar EOG channels vEOG and hEOG, according to adaptive Z-score thresholding.
	Finally, epochs were cut from 0.1s to 0.6s after stimulus onset.
	No baseline correction was performed since this affects the temporal covariance
	of the data, violating the Toeplitz structure assumption~\cite{Bijma2003}.

@@

  \subsubsection{\Acl{stbf} classifier}
	Before calculating the \ac{stbf}, the signal was downsampled to
	32Hz or twice the low-pass frequency 16Hz, resulting in 17 time samples
	between 0.1 and 0.6s. According to the Nyquist Theorem, more samples would not
	contain more information hence the minimum temporal resolution is chosen to reduce
	the dimensionality of the covariance and improve its covariance.
	The activation pattern is the difference between the averages of epochs in response to cued targets and the averages of those in response to non-cued targets.
	We constructed three variations of the spatiotemporal beamformer:
	\ac{stbf} with empirical covariance estimation (\textsc{stbf-emp}) as in
	\cref{sec:stbf-struct/methods/emp-cov}, \ac{stbf} with
	\ac{loocv}-shrunk covariance estimation (\textsc{stbf-shrunk}) as in
	\cref{sec:stbf-struct/methods/shrunk-cov}, and \ac{stbf} with
	Kronecker-Toeplitz structured covariance estimation (\textsc{stbf-struct}) with \ac{loocv} shrinkage for
	the Kronecker factors as in \cref{sec:stbf-struct/methods/struct-cov}.

@@

	\cref{fig:iterations} confirms these results for the \textsc{stbf-struct} classifier.
	Using more than one fixed-point iteration does not significantly improve the
	accuracy across the amounts of training data and the number of trials
	used for evaluation.
	Hence, only one iteration is used for the \textsc{stbf-struct} classifier, leading to a drastic speed-up of
	the training process.

@@

  \begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/accuracy.eps}
    \caption[Clasifier accuracy in function of available training data.]{%
      Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\cref{fig:stbf-struct/accuracy-ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}

@@

	The tables show that \textsc{stbf-struct} has a significant advantage over
	\textsc{stbf-shrunk} when the number of training blocks is low.
	This effect is present for 1-, 2- and 5-trial evaluation.
	This advantage decreases (the $p$-value increases) when
	adding more training blocks.
	Both \textsc{stbf-struct} and \textsc{stbf-shrunk} perform significantly better
	than \textsc{stbf-emp} for all evaluated settings.
	Compared to \textsc{xdawn+rg}, \textsc{stbf-struct} also has significantly
	higher accuracy in almost all evaluated settings, except when using only one training block.
	\textsc{stbf-shrunk} does not outperform \textsc{xdawn+rg} when training data is low but gains a significant advantage
	when using more training data.

@@

	\begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/training_time.eps}
    \caption[Classifier training time.]{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			\textsc{xdawn+rg}.}
		\label{fig:stbf-struct/training-time}
	\end{figure}

	\cref{fig:stbf-struct/training-time} shows that the training time of
	\textsc{stbf-struct} increases less steeply than that of \textsc{stbf-shrunk}
	and \textsc{stbf-emp}. The training time of all three \ac{stbf}-based classifiers is
	much lower than that of \textsc{xdawn+rg}, which appears nearly constant when using
	4, 8, 16, or 32 channels.

@@

	\subsection{Classification accuracy}
	As evidenced by \cref{fig:accuracy} and Tables \ref{tab:stbf-struct/p-values-1}-\ref{tab:stbf-struct/p-values-5}, the regularized classifiers \textsc{stbf-shrunk}
	and \textsc{stbf-struct} significantly improve the classification accuracy
	compared to the original \textsc{stbf-emp} for all numbers of training blocks
	indicated.
	We believe there are three reasons for this.
	First and foremost, the empirical covariance matrix in \textsc{stbf-emp} becomes
	ill-conditioned when the number of available training epochs is smaller than
	the number of features ($N<CS$), rendering its inversion with the
	Moore-Penrose pseudoinverse unstable.
	This is the case \textsc{stbf-emp} when $N=CS=32*17=544$, after which the
	accuracy of \textsc{stbf-emp} starts to increase.
	This effect is visible in \cref{fig:accuracy}, where the accuracy starts
	increasing when using more than four training blocks, amounting to 540 epochs.
	The noticeable dip in accuracy when using around 540 epochs can be explained by
	numerical effects in the pseudoinverse for very small
	eigenvalues~\cite{Blankertz2011, Raudys1998, Schaefer2004,
		Kraemer2009}.
	Regularization of the covariance matrix with shrinkage ensures that the
	covariance matrix is non-singular and better conditioned so it can stably be inverted.
	Second, covariance regularization introduces a trade-off between variance and bias of the model~\cite{Ledoit2004}.
	Better performance on unseen data can be achieved when some model variance is
	traded for extra bias.
	Regularization reduces extreme values present, as shown in
	\cref{fig:kronlda-covs}, resulting in a classifier with
	better generalization.
	Third, the true spatiotemporal covariance matrix may vary throughout \ac{bci}
	sessions, e.g., due to movement of the \ac{eeg}-cap, changing impedances of
	electrodes, subject fatigue, the introduction of new spatiotemporal noise
	sources, and other possible confounds.
	A regularized covariance matrix should better account for changes in true covariance.
	Note that the \ac{loocv} method in principle assumes that the covariances of
	the training data and unseen data are the same.
	Because the covariance might have changed for unseen data, the shrinkage
	estimate obtained with \ac{loocv} is probably still an
	underestimation of the optimal -- but unknown -- shrinkage coefficient that
	would yield the best classification accuracy for the unseen data.

	Another observation is the significantly better accuracy score of
	\textsc{stbf-struct} over \textsc{stbf-shrunk} when the amount of available training data is small.
	This property is an attractive advantage in a \ac{bci} setting since it is desirable to keep the calibration (training) phase as short as possible without losing accuracy.
	The accuracy advantage of the structured estimator is a consequence of the
	Kronecker-Toeplitz covariance structure, which is informative for the
	underlying process generating the epochs, if it is assumed that the \ac{eeg} signal
	is a linear combination of stationary activity generated by random dipoles in
	the brain with added noise~\cite{Munck1992, DeMunck2002, GonzalezNavarro2017}.
	Hence, \textsc{stbf-struct} can utilize this prior information to better estimate the inverse
	covariance.
	The increase in accuracy for small training set sizes can also be explained by the smaller number of parameters necessary to estimate the inverse covariance (see \cref{sec:stbf-struct/discussion/param-complex}), increasing the stability of matrix inversions.

	When compared to the state-of-the-art \textsc{xdawn+rg} classifier, we conclude
	that \textsc{stbf-struct} reaches similar accuracy when using only one block of
	training data.
	The authors suspect this is due to both
	classifiers having insufficient training information to reach
	satisfactory classification accuracy.
	When more data are available, \textsc{stbf-struct} reaches significantly better accuracies.
	Combined with the benefits laid out in \cref{sec:stbf-struct/discussion/param-complex}, this
  makes it an attractive option for \ac{erp} classification.
	\textsc{stbf-shrunk} does not show decisive accuracy improvements over
	\textsc{xdawn+rg} using a few training blocks, but this improves as the training data increases.

@@

	Second, structured estimation has better time complexity.
	Covariance estimation and inversion occupy the largest part of the \ac{stbf} training time.
	For \textsc{stbf-emp} and \textsc{stbf-shrunk}, the time complexity of this process is $\mathcal{O}(NC^2S^2+C^3S^3)$.
	Thanks to Property~\ref{prop:stbf-struct/inverse-kronecker}, the complexity can be reduced to
	$\mathcal{O}(NS^2S^2+C^3+S^3)$ for the structured estimator of \textsc{stbf-struct}.
	The results presented in \cref{fig:stbf-struct/training-time} confirm these
	calculations.
	It can be observed that the training time of \textsc{stbf-struct} stays low compared to \textsc{stbf-emp} and \textsc{stbf-shrunk} when dimensionality increases.

	The results shown in \cref{fig:stbf-struct/training-time} also confirm that the
	\ac{stbf}-based estimators are very fast to train compared to the
	state-of-the-art estimator \textsc{xdawn+rg}, which confirms the results in~\cite{Wittevrongel2016}.
	Since the training times of all \ac{stbf}-based classifiers are already in
	the order of tenths of seconds, the question arises whether the
	improvements achieved by using the structured estimator would be relevant in
	practice.
	However, the authors believe that these results could significantly impact some
	use cases of the spatiotemporal beamformer, like high spatial or temporal resolution \ac{erp} analyses.
	One example is single-trial \ac{erp} analysis with a high-temporal
	resolution to extract \ac{erp} time features.
	Such higher-resolution analyses can later be incorporated into an \ac{erp}
	classification framework.
	In addition, the speed-up provided by structured estimation yields a faster
	off-line evaluation of the \ac{stbf} \ac{erp} classifier, where often multiple cross-validation folds, subjects, and hyperparameter settings need to be explored, which can quickly increase runtime.
	Improvements in computation speed and memory usage can remove the need for dedicated computation hardware and enable running group analyses on a personal computer.

@@

	\section{Conclusion}
	While it is possible to regularize the spatiotemporal \ac{lcmv} beamformer
	classifier for \ac{erp} detection with other methods such as by employing feature selection,
	by adding regularizing penalties to the cost
	function beamforming problem, or by crafting a cleaner activation pattern, our work focused on
	estimation methods for the spatiotemporal covariance.
	We introduced a covariance estimator using adaptive shrinkage and an
	estimator exploiting prior knowledge about the spatiotemporal nature of the \ac{eeg}
	signal.
	We compared these estimators with the original spatiotemporal
	beamformer and a state-of-the-art method in an off-line P3 detection task.
	Our results show that the structured estimator performs better when training data are sparsely available and that it can be computed faster and with substantially less memory usage.
	Since these algorithms are not paradigm-specific,  the conclusions can be generalized to
	other \ac{erp}-based \ac{bci} settings.

>>>>

	\subsubsection{Shrunk covariance estimation}
	\label{sec:stbf-struct/methods/shrunk-cov}
	The shrinkage covariance estimator creates a better conditioned inversion matrix problem and generally performs better when applied to unseen data.
	The estimators for the covariance and inverse covariance are given by:
	\begin{equation}
    \hat{\mat{C}}_\alpha =
    (1-\alpha) \hat{\mat{C}}_\text{emp}
    + \alpha\frac{\text{Tr}(\hat{\mat{C}}_\text{emp})}{CS}\mathbb{I}
		\label{eq:shrinkage}
	\end{equation}
	\begin{equation}
    \widehat{\mat{C}^{-1}}_\alpha =
    \hat{\mat{C}}^+_\alpha
		\label{eq:stbf-struct/shrinkage-inv}
	\end{equation}
	with $0<\alpha<1$.
	Analogous to $L_2$ regularization of the beamforming problem,
	shrinkage reduces the ratio between the smallest and largest eigenvalues
	of the covariance matrix by strengthening the diagonal.
	\cref{fig:kronlda-covs}c and \cref{fig:kronlda-covs}d respectively show examples of the
	shrunk estimator of the covariance and the inverse covariance matrices.

@@

	The \ac{eeg} recorded at 2048Hz was re-referenced off-line to the average of the mastoids.
	The reference electrodes were dropped from the analysis.
	Data were subsequently filtered between 0.5Hz and 16Hz using forward-backward
	filtering with a fourth-order Butterworth IIR filter.
	The \ac{eeg} signal was corrected for ocular artifacts using Independent Component
	Analysis (ICA) by rejecting components that correlated with the bipolar EOG
  channels vEOG and hEOG, according to adaptive Z-score
  thresholding.\todo{details? threshold for rejection?}
	Finally, epochs were cut from 0.1s to 0.6s after stimulus onset.
	No baseline correction was performed since this affects the temporal covariance
	of the data, violating the Toeplitz structure assumption~\cite{Bijma2003}.

@@

  \subsubsection{\Acl{stbf} classifier}
	Before calculating the \ac{stbf}, the signal was downsampled to
	32Hz or twice the low-pass frequency 16Hz, resulting in 17 time samples
	between 0.1 and 0.6s. According to the Nyquist Theorem, more samples would not
	contain more information hence the minimum temporal resolution is chosen to reduce
	the dimensionality of the covariance and improve its condition number.
	The activation pattern is the difference between the averages of epochs in response to cued targets and the averages of those in response to non-cued targets.
	We constructed three variations of the spatiotemporal beamformer:
	\ac{stbf} with empirical covariance estimation (\textsc{stbf-emp}) as in
	\cref{sec:stbf-struct/methods/emp-cov}, \ac{stbf} with
	\ac{loocv}-shrunk covariance estimation (\textsc{stbf-shrunk}) as in
	\cref{sec:stbf-struct/methods/shrunk-cov}, and \ac{stbf} with
	Kronecker-Toeplitz structured covariance estimation (\textsc{stbf-struct}) with \ac{loocv} shrinkage for
	the Kronecker factors as in \cref{sec:stbf-struct/methods/struct-cov}.

@@

	\cref{fig:iterations} confirms these results for the \textsc{stbf-struct} classifier.
	Using more than one fixed-point iteration does not significantly improve the
	accuracy across the amounts of training data and the number of trials
  used for evaluation\todo{qualitative}.
	Hence, only one iteration is used for the \textsc{stbf-struct} classifier, leading to a drastic speed-up of
  the training process\todo{qualitative}.

@@

  \begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/accuracy.eps}
    \caption[Clasifier accuracy in function of available training data.]{%
      Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\cref{fig:stbf-struct/accuracy-ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}
  \todo{the legend does not correspond to the text (method names are
  different)}

@@

	The tables show that \textsc{stbf-struct} has a significant advantage over
	\textsc{stbf-shrunk} when the number of training blocks is low.
  This effect is present for 1-, 2- and 5-trial evaluation\todo{qualitative}.
	This advantage decreases (the $p$-value increases) when
  adding more training blocks\todo{qualitative}.
	Both \textsc{stbf-struct} and \textsc{stbf-shrunk} perform significantly better
  than \textsc{stbf-emp} for all evaluated settings\todo{qualitative}.
	Compared to \textsc{xdawn+rg}, \textsc{stbf-struct} also has significantly
	higher accuracy in almost all evaluated settings, except when using only one
  training block\todo{qualitative}.
	\textsc{stbf-shrunk} does not outperform \textsc{xdawn+rg} when training data
  is low but gains a significant advantage	when using more training
  data\todo{qualitative}.

@@

	\begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/training_time.eps}
    \caption[Classifier training time.]{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			\textsc{xdawn+rg}.}
		\label{fig:stbf-struct/training-time}
	\end{figure}
  \todo{the legend does not correspond to the text (method names are
  different)}

	\cref{fig:stbf-struct/training-time} shows that the training time of
	\textsc{stbf-struct} increases less steeply than that of \textsc{stbf-shrunk}
	and \textsc{stbf-emp}. The training time of all three \ac{stbf}-based classifiers is
  much lower\todo{qualitative} than that of \textsc{xdawn+rg}, which appears nearly constant when using
	4, 8, 16, or 32 channels.

@@

	\subsection{Classification accuracy}
	As evidenced by \cref{fig:accuracy} and Tables \ref{tab:stbf-struct/p-values-1}-\ref{tab:stbf-struct/p-values-5}, the regularized classifiers \textsc{stbf-shrunk}
	and \textsc{stbf-struct} significantly improve the classification accuracy
	compared to the original \textsc{stbf-emp} for all numbers of training blocks
  indicated\todo{qualitative}.
	We believe there are three reasons for this.
	First and foremost, the empirical covariance matrix in \textsc{stbf-emp} becomes
	ill-conditioned when the number of available training epochs is smaller than
	the number of features ($N<CS$), rendering its inversion with the
	Moore-Penrose pseudoinverse unstable.
	This is the case \textsc{stbf-emp} when $N=CS=32*17=544$, after which the
	accuracy of \textsc{stbf-emp} starts to increase.
	This effect is visible in \cref{fig:accuracy}, where the accuracy starts
	increasing when using more than four training blocks, amounting to 540 epochs.
	The noticeable dip in accuracy when using around 540 epochs can be explained by
	numerical effects in the pseudoinverse for very small
	eigenvalues~\cite{Blankertz2011, Raudys1998, Schaefer2004,
		Kraemer2009}.
	Regularization of the covariance matrix with shrinkage ensures that the
	covariance matrix is non-singular and better conditioned so it can stably be inverted.
	Second, covariance regularization introduces a trade-off between variance and bias of the model~\cite{Ledoit2004}.
	Better performance on unseen data can be achieved when some model variance is
	traded for extra bias.
	Regularization reduces extreme values present, as shown in
	\cref{fig:kronlda-covs}, resulting in a classifier with
	better generalization.
	Third, the true spatiotemporal covariance matrix may vary throughout \ac{bci}
	sessions, e.g., due to movement of the \ac{eeg}-cap, changing impedances of
	electrodes, subject fatigue, the introduction of new spatiotemporal noise
	sources, and other possible confounds.
	A regularized covariance matrix should better account for changes in true covariance.
	Note that the \ac{loocv} method in principle assumes that the covariances of
	the training data and unseen data are the same.
	Because the covariance might have changed for unseen data, the shrinkage
	estimate obtained with \ac{loocv} is probably still an
	underestimation of the optimal -- but unknown -- shrinkage coefficient that
	would yield the best classification accuracy for the unseen data.

	Another observation is the significantly better accuracy score of
	\textsc{stbf-struct} over \textsc{stbf-shrunk} when the amount of available
  training data is small\todo{qualitative}.
	This property is an attractive advantage in a \ac{bci} setting since it is desirable to keep the calibration (training) phase as short as possible without losing accuracy.
	The accuracy advantage of the structured estimator is a consequence of the
	Kronecker-Toeplitz covariance structure, which is informative for the
	underlying process generating the epochs, if it is assumed that the \ac{eeg} signal
	is a linear combination of stationary activity generated by random dipoles in
	the brain with added noise~\cite{Munck1992, DeMunck2002, GonzalezNavarro2017}.
	Hence, \textsc{stbf-struct} can utilize this prior information to better estimate the inverse
	covariance.
  The increase in accuracy for small training set sizes\todo{qualitative} can also be explained by the smaller number of parameters necessary to estimate the inverse covariance (see \cref{sec:stbf-struct/discussion/param-complex}), increasing the stability of matrix inversions.

	When compared to the state-of-the-art \textsc{xdawn+rg} classifier, we conclude
	that \textsc{stbf-struct} reaches similar accuracy when using only one block of
  training data\todo{qualitative}.
	The authors suspect this is due to both
	classifiers having insufficient training information to reach
	satisfactory classification accuracy.
	When more data are available, \textsc{stbf-struct} reaches significantly
  better accuracies\todo{qualitative}.
	Combined with the benefits laid out in \cref{sec:stbf-struct/discussion/param-complex}, this
  makes it an attractive option for \ac{erp} classification.
	\textsc{stbf-shrunk} does not show decisive accuracy improvements over
	\textsc{xdawn+rg} using a few training blocks, but this improves as the
  training data increases\todo{qualitative}.

@@

	Second, structured estimation has better time complexity.
	Covariance estimation and inversion occupy the largest part of the \ac{stbf} training time.
	For \textsc{stbf-emp} and \textsc{stbf-shrunk}, the time complexity of this process is $\mathcal{O}(NC^2S^2+C^3S^3)$.
	Thanks to Property~\ref{prop:stbf-struct/inverse-kronecker}, the complexity can be reduced to
	$\mathcal{O}(NS^2S^2+C^3+S^3)$ for the structured estimator of \textsc{stbf-struct}.
	The results presented in \cref{fig:stbf-struct/training-time} confirm these
	calculations.
	It can be observed that the training time of \textsc{stbf-struct} stays low
  compared to \textsc{stbf-emp} and \textsc{stbf-shrunk} when dimensionality
  increases\todo{qualitative}.

	The results shown in \cref{fig:stbf-struct/training-time} also confirm that the
	\ac{stbf}-based estimators are very fast to train compared to the
	state-of-the-art estimator \textsc{xdawn+rg}, which confirms the results
  reported by~\textcite{Wittevrongel2016}.
	Since the training times of all \ac{stbf}-based classifiers are already in
	the order of tenths of seconds, the question arises whether the
	improvements achieved by using the structured estimator would be relevant in
	practice.
	However, the authors believe that these results could significantly impact some
	use cases of the spatiotemporal beamformer, like high spatial or temporal
  resolution \ac{erp} analyses (e.g., $C>>32, S>>256$).
	One example is single-trial \ac{erp} analysis with a high-temporal
	resolution to extract \ac{erp} time features.
	Such higher-resolution analyses can later be incorporated into an \ac{erp}
	classification framework.
	In addition, the speed-up provided by structured estimation yields a faster
	off-line evaluation of the \ac{stbf} \ac{erp} classifier, where often multiple cross-validation folds, subjects, and hyperparameter settings need to be explored, which can quickly increase runtime.
	Improvements in computation speed and memory usage can remove the need for dedicated computation hardware and enable running group analyses on a personal computer.

@@

	\section{Conclusion}
	While it is possible to regularize the spatiotemporal \ac{lcmv} beamformer
	classifier for \ac{erp} detection with other methods such as by employing feature selection,
	by adding regularizing penalties to the cost
	function beamforming problem, or by crafting a cleaner activation pattern, our work focused on
	estimation methods for the spatiotemporal covariance.
	We introduced a covariance estimator using adaptive shrinkage and an
	estimator exploiting prior knowledge about the spatiotemporal nature of the \ac{eeg}
	signal.
	We compared these estimators with the original spatiotemporal
	beamformer and a state-of-the-art method in an off-line P3 detection task.
	Our results show that the structured estimator performs better when training
  data are sparsely available and that it can be computed faster and with
  substantially less memory usage\todo{qualitative}.
	Since these algorithms are not paradigm-specific,  the conclusions can be generalized to
	other \ac{erp}-based \ac{bci} settings.
